### 2016-06-01 thesis/methods/methods.tex
tmp commit

The gene probe IDs in Creighton data were converted into gene symbols using the \textit{hgu133a.db} package in \gls{r}.
Where there was a duplicated gene, appropriate gene data was chosen to represent that particular gene by using the \texttt{collapseRows} function in the \textit{WGCNA} package in \gls{r}.
All of the *** obesity associated genes from  \cref{subsec:fmobsgene} were selected from the data.

@@

When there was more than 799 gene probes in the list of significant genes, the top 799 gene probes were selected from the list.
This list of 799 gene probes represented the obesity associated metagene for that dataset.

For each gene probe set, the gene probes that were common with the obesity associated genes identified by \citet{Creighton2012} were selected and used as a separate gene probe set.
There were eight metagenes in total after this process: four gene probe sets from the datasets from \cref{subsec:subdatadeg}, and four gene probe sets that were in common with the obesity associated genes from the \citet{Creighton2012} study.

@@

For each of the eight gene probe sets identified in \cref{subsec:crdeg}, the gene probe IDs were converted into gene symbols using the \textit{hgu133a.db} package in \gls{r}.
Any duplicates and any gene symbols that were not present in both the Creighton data and the ICGC data were removed from the gene probe set.

@@

@@

The gene probe IDs in the Creighton data were converted into gene symbols using the \textit{hgu133a.db} package in \gls{r}.
Where there was a duplicated gene in the data, appropriate gene data was chosen to represent that particular gene by using the \texttt{collapseRows} function in the \textit{WGCNA} package in \gls{r}.

For each BMI gene probe set identified in \cref{sec:deg}, relevant genes were taken from the Creighton data.
The data was then standardised so all of the genes had a mean ($\mu$) of 0 and standard deviation ($\sigma$) of 1.

>>>>

The gene probe IDs in Creighton data were converted into gene symbols using the \textit{hgu133a.db} package in \gls{r}.
Where there was a duplicated gene, appropriate gene data was chosen to represent that particular gene by using the \texttt{collapseRows} function in the \textit{WGCNA} package in \gls{r}.
All of the *** obesity associated genes from  \cref{subsec:fmobsgene} were selected from the data.
The data was then standardised so that each of the genes had a mean ($\mu$) of 0 and a standard deviation ($\sigma$) of 1.

@@

When there was more than 799 gene probes in the list of significant genes, the top 799 gene probes were selected from the list.
This list of 799 gene probes represented the gene probes that were associated with obesity  for that dataset.

\subsection{Common gene probes from the \citet{Creighton2012} study}
\label{subsec:crol}

For each gene probe set, the gene probes that were common with the obesity associated genes identified by \citet{Creighton2012} were selected and used as a separate gene probe set.
There were eight gene probe sets in total after this process: four gene probe sets from the datasets from \cref{subsec:subdatadeg}, and four gene probe sets that were in common with the obesity associated genes from the \citet{Creighton2012} study.

%TODO: add a table summarizing how many genes were in each gene probe set

@@

For each of the eight gene probe sets identified in \cref{subsec:crdeg,subsec:crol}, the gene probe IDs were converted into gene symbols using the \textit{hgu133a.db} package in \gls{r}.
Any duplicates and any gene symbols that were not present in both the Creighton data and the ICGC data were removed from the gene probe set.

@@

The gene probe IDs in Creighton data were converted into gene symbols using the \textit{hgu133a.db} package in \gls{r}.
Where there was a duplicated gene, appropriate gene data was chosen to represent that particular gene by using the \texttt{collapseRows} function in the \textit{WGCNA} package in \gls{r}.
For each gene probe sets identified in \cref{subsec:crdeg,subsec:crol}, the gene probes were selected from this data.
The data was then standardised so that each of the genes had a mean ($\mu$) of 0 and a standard deviation ($\sigma$) of 1.

SVD was applied to the standardised data, and the first eigenvector of the decomposed matrix was used as the sample metagene score for that gene probe set.
The \gls{metagene} scores were ranked based on the number of samples in the data (*** samples in Creighton data), and the scores ranged from 0 to 1.

@@

For each \gls{metagene} scores in \cref{subsec:bmimetagen} were plotted together with the gene expression of the associated gene probes for each sample on a heatmap.
The samples in the heatmap were ordered based on their ranked \gls{metagene} scores.
To have a better colour scales in the heatmap, any expression values that were greater than 3 or less than -3 were assigned the value of 3 and -3, respectively.
